\documentclass[11pt]{article}
\usepackage{array, xcolor}
\usepackage[margin=2cm, bottom=2em]{geometry}
\usepackage{nopageno}
\usepackage{enumitem}

\setlength{\voffset}{-0.75in}
\sloppy
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{blindtext}
\usepackage{lastpage}
\cfoot{\thepage\ of \pageref{LastPage}}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
 
\title{\bfseries\Huge Toby Bessant - Curriculum Vitae\vspace{-2em}}
\date{}

\definecolor{lightgray}{gray}{0.2}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}
\pagebreak
 
\begin{document}
% remove line-broken words
\sloppy
\maketitle
\thispagestyle{fancy}
\begin{center}
\begin{tabular}[]{rl}
Date of Birth & 13/04/1998\\
Telephone     &07538 955566\\
Email            & toby.bessant@tobybessant.co.uk\\
GitHub 	    & github.com/tobybessant\\
Portfolio        & tobybessant.co.uk\\
\end{tabular}
\end{center}
\vspace*{-19pt}
\section*{Profile}
\vspace*{-10pt}
Progressive and client-focused full-stack developer experienced in producing robust applications across an array of technologies. Demonstrable understanding of software development fundamentals, in addition to a multitude of newer frameworks and libraries. Undertaken an industry placement year working under agile methodologies to integrate \& automate business web-applications. Always exploring new ideas through tangible projects including a mobile tenancy communication platform, web-based multi-player typing game, and a noise-based procedural terrain generator.
 \vspace*{-10pt}
\section*{Professional Experience}
\vspace*{-10pt}
\begin{tabular}{L!{\VRule}R}
2018--2019 & {\bf Business Applications Developer} | A2Z Cloud\\
                   & Placement year taken as part of my degree. Configured, automated, and integrated various Zoho  and external business applications.
                      \vspace*{-7pt}
                      \begin{itemize}[noitemsep]
                      \item Developed {\bf NodeJS} middlewares to sync and map relational-database records to formats received by business applications.
                      \item Hosted applications using {\bf AWS} lambda.
                      \item Used various REST API's \& webhooks to connect services.
                      \item Attended and ran weekly {\bf client meetings}, both for requirements gathering and app demos.
                      \item Took part in daily {\bf scrum} meetings, even having the opportunity to run a scrum meeting when my manager was unavailable.
                      \end{itemize}
                      \\ [8pt]
                      
2015--2016 & {\bf Customer Assisstant} | The Regal Stowmarket\\
                   & Part-time job during college to improve confidence and start earning some personal finances. 
                      \vspace*{-7pt}
                      \begin{itemize}[noitemsep]
                      \item Selling box office tickets, answering customer calls, working behind the bar
                      \item Developed good communication skills due to small team of 3 at all times.
                      \item Small team size meant I took part in marketing decisions and am proud to say that their growth led to plans of expansion after my departure.
                      \end{itemize}
                      \\
\end{tabular}

\section*{Education}
\begin{tabular}{L!{\VRule}R}
2016--2020 & {\bf Computing \& Games Development BSc (Hons), University of Plymouth.}\\
                   & Predicted to graduate with first-class honours\\
[5pt]
2014--2016 & {\bf A-Levels, Suffolk One Sixth-form College.}\\
                   & Computing: D,   Sociology: B,  Psychology: D,   Ancient History AS: D\\
[5pt]
2009--2014 & {\bf GCSE's, Stradbroke High School.}\\
[5pt]
                   &
                     \begin{tabular}[]{lll}
                     English: B &  Core Science: B & ICT: Pass \\ 
                     Maths: B & Additional Science: B & History: A \\  
                     Religious Studies: A*  & Business Studies: B & Graphics: C\\
                     \end{tabular}
\end{tabular}

\pagebreak
% remove line-broken words
\sloppy
\vspace*{2cm}
\section*{Skills Profile}
\vspace*{-5pt}
{\bf Software development: } Agile (scrum), SOLID principles, GoF Design Patterns, TDD\\
{\bf Languages: } C\#, Java, JavaScript, HTML/CSS\\
{\bf Web frameworks: } TypeScript, Express, TypeORM, Mocha, VueJS, Angular8, SCSS, Cordova, Ionic\\
{\bf Database: } SQLServer, MongoDB\\
{\bf Version control: } Git, GitHub, Bitbucket\\
{\bf CI/CD: } Docker, Azure Pipelines, Heroku\\[5pt]
As a result of my university degree I have experience developing in a wide range of languages, environments, and disciplines. The first two years of my degree were centred around building a foundation for my programming skills, using C\# and Java to demonstrate SOLID principles and implement design patterns to solve problems. As I have matured as a developer my primary interest has shifted towards full-stack web development. In my own time I started to teach myself about web development, and carried these skills into my final year at university. Since then, I have experience developing in JavaScript and TypeScript to produce APIs \& persistence layers, communicating to both MongoDB and relational databases. My front-end development experience spans the use of VueJS and Angular8, for desktop web applications and native mobile applications. I have experience using Git in both individual and team settings, performing and receiving pull-requests and code reviews with my colleagues.
\newline\newline
Between my second and third years of university, I was able to use the skills I had learnt in an industry environment - automating and integrating business web-applications for clients. Working in an agile environment meant I was involved with scrum meetings, and directly demonstrating my solutions to clients over online meetings on a weekly basis. My placement gave me skills in programming and debugging in a web environment, in addition to working with APIs, databases, and building integration middleware. This middleware was often hosted on AWS which I would help configure. I would also be on the client support portal, emailing and calling clients to assist them with any problems they were experiencing. On a personal level, my placement year improved my confidence which in turn has helped with my ability to approach new challenges.
\newline\newline
In addition to the skills outlined above, I have experience using C\# to develop experience-based projects in Unity3D - allowing me to utilise my programming knowledge to make games, and VR experiences. During my final year of university I used C++ and OpenGL to build various graphics rendering applications;  a model-loader to parse and render the data for 3D model files, and an application to procedurally generate \& render virtual terrains using noise functions.

\section*{Interests}
\vspace*{-10pt}
Outside of software development I have a keen interest in reading fiction books, particularly of the crime-fiction genre. I enjoy it because it provides a way for me to be analytical and test my problem solving abilities in an atypical way. In addition, I enjoy learning about ancient history - particularly Ancient Rome and Ancient Greece, as these eras of human history are responsible for many of our traditions today. In my spare time I play guitar, which feeds into an active interest in music - something which has had a large influence on my life.


\section*{References}
\vspace*{-10pt}
References available on request.

\cfoot{\thepage\ of \pageref{LastPage}}
\end{document}